---
title: "IDS 2935: Historical Narratives"
date: "updated: `r Sys.Date()`"
header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
mainfont: SourceSansPro
geometry: margin=1in
fontsize: 12pt
linkcolor: blue
urlcolor: blue
output:
  pdf_document: default
  html_document:
    df_print: paged
  rmdformats::robobook: default
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## **Pre-Class Preparation (Instructor):  **&

1. Email Reminder

## **Bring to Class:**  

1. Roster
2. Syllabi
3. Chocolates
4. Masks
5. Hand Sanitizer
6. Copy of the Book

## Objectives and Competencies:   

1. 
2. 
3. 

## Pre-class Preparation (Students):


### **Readings**

1. None

### **Online Lectures:**  

1. None
        

## Class Outline


```{r timer, echo=FALSE}

Block1_intro <- 5
Block1_breakout <- 10
Break <- 0
return_results <- 10
intro_next_session <- 15
questions <- 5  
  
total_time <- 
  Block1_intro + 
  Block1_breakout + 
  Break + 
  return_results + 
  questions +
  intro_next_session 


time_remain <- 150 - total_time
```

### **Intro: ** (`r Block1_intro` min)

1. Most Europeans entered the tropics in a political and social climate of colonization and exploitation (of people, their culture, and natural resources). 

2. That shapes their perceptions of both tropical environments and the people they encountered.

3. These people wrote home about what they saw, and brought things back with them.  

4. These stories percolate through society and are reflected back by authors and artists for consumption by the public.

5. This reinforces and helps perpetuate the first perceptions (and misconceptions).

### **Breakout** (`r Block1_breakout` min): Chocolate

### **Return and discuss breakout results** (`r return_results` min)


### **Break**  (`r Break` min)    

### **Breakout 2**  (`r intro_next_session` min)      

### Closing Remarks/Questions (`r questions` min)

6. Fill out the Survey in Canvas as Assignment 1!


### Free Time

There are `r time_remain` min remaining that can be used to answer questions

# Additional Resources and Reading Mateirals

1. [The Real Price of a Chocolate Bar: West Africa’s Rainforests - Yale e360](https://e360.yale.edu/features/the-real-price-of-a-chocolate-bar-west-africas-rainforests)
2. [Ghana Exports](https://tradingeconomics.com/ghana/exports-by-category)
3. [Ivory Coast Exports](https://tradingeconomics.com/ivory-coast/exports-by-category)
4. [Leading Cocoa Exporters](https://www.statista.com/statistics/1112357/global-leading-exporters-of-cocoa-beans/)


