---
title: "IDS 2935: Course Introduction"
date: "updated: `r Sys.Date()`"
header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
mainfont: SourceSansPro
geometry: margin=1in
fontsize: 12pt
linkcolor: blue
urlcolor: blue
output:
  pdf_document: default
  html_document:
    df_print: paged
  rmdformats::robobook: default
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## **Pre-Class Preparation (Instructor):  **&

1. Email Reminder

## **Bring to Class:**  

1. Roster
2. Syllabi
3. Chocolates
4. Masks
5. Hand Sanitizer
6. Copy of the Book

## Objectives and Competencies:   

1. Introduce the class and challenges of tropical rain forest conservation 
2. Review the Syllabus
3. Ask students to fill out the online survey


**<<Revision for v 2.0: have 1/2 the class do the survey for "tropical rain forest" and the other half do the words that come to mind with "jungle" - would be really interesteing to compare the differences that come to mind, and is a good lead-in to Jungle being defined by the oprotish officers.">>** 

## Pre-class Preparation (Students):


### **Readings**

1. None

### **Online Lectures:**  

1. None
        

## Class Outline


```{r timer, echo=FALSE}

Block1_intro <- 5
Block1_breakout <- 10
Break <- 0
return_results <- 10
intro_next_session <- 15
questions <- 5  
  
total_time <- 
  Block1_intro + 
  Block1_breakout + 
  Break + 
  return_results + 
  questions +
  intro_next_session 


time_remain <- 50 - total_time
```

### **Topic 1: Free List** (`r Block1_intro` min)

* Brainstorm as many words as possible when you hear the words "Tropical Rain Forest". Write them down (or save them on a cell phone/laptop). Explain they will need this for the survey they need to fill out online.

### **Breakout** (`r Block1_breakout` min): Chocolate

* Introduce yourselves to each other (name, major, where from), and without looking at your cell phones or computers see if you can answer this question:

  * Q1: What is the primary ingredient in Chocolate?
  * Q2: Where (what countries) are the primary producers of this ingredient? 


### Return and discuss breakout results (`r return_results` min)

* Review the answers, set up Cacao being a good example of the challenges being faced: hugely important crop in terms of national exports and family income, threatened by climate change, leading to deforestation, and driven by an increasing demand. 

* Studying these challenges is what this class is all about.

### Next Section  (`r intro_next_session` min)      

*Syllabus and Course overview
* Remind people this is an experiment, and also that thibngs change quickly (deforestation, fires, etc) so there will be some changes on the fly. Check syllabus frequently

* "Some of you may be new to UF and so may not know what Office Hours are. They're an opportunity to..."

* "This class has very little work out side of class, easy reading, and no tests. In return I ask that you come to class committed to engage and enjoy yourself. This class will (I hope) be the least stressful one you have all semester. That doesn't necessarily mean it will be the easiest - in fact it may be quite challenging sometimes - but I hope that won't be too stressful. That's my commitment to you."


### Closing Remarks/Questions (`r questions` min)

6. Fill out the Survey in Canvas as Assignment 1!


### Free Time

There are `r time_remain` min remaining that can be used to answer questions

# Additional Resources and Reading Mateirals

1. [The Real Price of a Chocolate Bar: West Africa’s Rainforests - Yale e360](https://e360.yale.edu/features/the-real-price-of-a-chocolate-bar-west-africas-rainforests)
2. [Ghana Exports](https://tradingeconomics.com/ghana/exports-by-category)
3. [Ivory Coast Exports](https://tradingeconomics.com/ivory-coast/exports-by-category)
4. [Leading Cocoa Exporters](https://www.statista.com/statistics/1112357/global-leading-exporters-of-cocoa-beans/)

