---
title: "IDS_2935: ------"
date: "updated: `r Sys.Date()`"
header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
mainfont: SourceSansPro
geometry: margin=1in
fontsize: 12pt
linkcolor: darkmidnightblue
urlcolor: darkmidnightblue
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \fancyhead[R]{Syllabus, p. \thepage}
- \fancyhead[L]{IDS 2935 - Rain Forests (`r format(Sys.time(), '%Y')`)}
- \usepackage[default]{sourcesanspro}
- \usepackage{parskip}
- \usepackage{xcolor}
- \AtBeginDocument{\let\maketitle\relax}
# - \usepackage{sectsty} \allsectionsfont{\raggedright}
- \usepackage{sectsty} \sectionfont{\centering}
- \usepackage{titlesec}
- \usepackage{sectsty} \sectionfont{\centering\color{darkmidnightblue}}
- \usepackage{sectsty} \subsectionfont{\color{darkmidnightblue}}
- \titlespacing{\section}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \titlespacing{\subsubsection}{0pt}{12pt plus 2pt minus 1pt}{0pt plus 1pt minus 1pt}
- \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
- \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
output:
  pdf_document: default
  html_document:
    df_print: paged
  rmdformats::robobook: default
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Pre-Class Preparation (Instructor):  

1. Email Reminder
2.
3. **Bring to Class:**  
*
*
*

## Objectives and Competencies:   

1.
2.
3.


## Pre-class Preparation (Students):


### **Readings**
1.
2.
3.

### **Online Lectures:**  

1.
2.
3.
        

## Class Outline


```{r timer, echo=FALSE}

Block1_intro <- 25
Block1_breakout <- 30
Break <- 10
return_results <- 20
questions <- 10
intro_next_session <- 10
  
  
total_time <- 
  Block1_intro + 
  Block1_breakout + 
  Break + 
  return_results + 
  questions +
  intro_next_session 


time_remain <- 50 - total_time
```



### **Topic 1 Overview: Paperless Data Collection** (`r t1_overview` min)

### Breakout

**Breakout (`r breakout1` min): ** Paperless data collection with Epicollect


### Break (`r snack_break` min)

### Return and discuss breakout results

1. **Returning results & Take-home message (`r breakout1_return` min)** 

2. **Take-home message:** Reinforce value of paperless data collection
      
### Free Time

There are `r time_remain` min remaining that can be used to -----

# Additional Resources and Reading Mateirals

1.
2.
3.

